Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle structure

### 2017-05-31 documents/TriangleScenarioArXiv/ts.tex
improved discussion of measures of non-classicality

\begin{document}
    \title{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure}
    \author{Thomas C. Fraser}
    \email{tcfraser@tcfraser.com}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
    \affiliation{University of Waterloo, Waterloo, Ontario, Canada, N2L 3G1}
    \author{Elie Wolfe}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
    % \email{ewolfe@perimeterinstitute.ca}
    \date{\today}
    \begin{abstract}
        It has long been recognized that certain quantum correlations are often incompatible with particular assumption about classical causal structure. Such correlations are sometimes termed non-local, although they are more accurately termed non-classical, as the presence of correlations certifies the genuinely non-classical nature of a causal setup in a device-independent fashion.  Whenever a quantum correlation violates a causal compatibility inequality (e.g. a Bell inequality) then the correlation is witnessed as non-classical. Any constraint which is satisfied by all correlations which \textit{are} classically compatible with a given causal structure defines a causal compatibility criterion. Such criteria were recently were recently derived for the Triangle structure [\href[pdfnewwindow]{http://arxiv.org/abs/1609.00672}{arXiv:1609.00672}] in the form of polynomial inequalities, begging the question: do any of those inequalities admit violation by quantum correlations? Numerical investigation suggests not, and we further conjecture that the set of correlations admitted by the classical Triangle structure is equivalent to the set of correlations admitted by its quantum generalization whenever the three observable variables are binary. Our main contribution in this work, however, is the derivation of new causal compatibility inequalities for the Triangle structure which \textit{do} admit quantum violation. We conclude by considering the possibility of quantum resources potentially qualitatively different from those known previously.
    \end{abstract}
    \maketitle
    \tableofcontents
    % \setlength{\parskip}{1em}

@@

    \begin{figure}
    \begin{center}
        \begin{minipage}[t]{.48\textwidth}
            \centering
            \scalebox{1.0}{\input{../../figures/causal_structures/bell_scenario}}
            \caption{The Bell structure consisting of two observers $\p{A}, \p{B}$ together with measurement settings $S_{\p{A}}$ and $S_{\p{B}}$ respectively. The shared hidden variable is labeled $\la$.}
            \label{fig:bell_scenario}
        \end{minipage}\hspace{0.04\textwidth}%
        \begin{minipage}[t]{.48\textwidth}
            \centering
            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure}}
            \caption{The casual structure of the Triangle structure. Three variables $A,B,C$ are observable, while $X, Y, Z$ are latent variables.}
            \label{fig:triangle_structure}
        \end{minipage}
    \end{center}
    \end{figure}
    \section{Triangle Structure}
    \label{sec:triangle_structure}

@@

    \section{Triangle Structure Inequalities}
    \label{sec:found_inequalities}

    \Cref{sec:causal_compatibility} defined causal compatibility inequalities while \cref{sec:fritz_distribution} recalled and discussed the Fritz distribution together with a brief summary of its incompatibility with the Triangle Structure. Heretofore, there were no known causal compatibility inequalities for the Triangle Structure that were capable of witnessing the non-classicality of any quantum distributions~\cite{Inflation}. By leveraging the incompatibility of the Fritz distribution~\cite{Fritz_2012} and tools provided by the Inflation Technique~\cite{Inflation}, we have obtained numerous causal compatibility inequalities for the Triangle Structure that are violated by the Fritz distribution. A representative sample of these inequalities are presented here. The methods used to derive these inequalities are largely based on the Inflation Technique~\cite{Inflation}. A summary of the Inflation Technique and other methods used will be deferred to \cref{sec:inflation_technique} where unfamiliar readers will find a succinct yet sufficient presentation of the requisites.

    The first causal compatibility inequality is reported below:
    \begin{equation*}
    \begin{gathered}
    \eq\label{eq:ww_ineq}
    2P_{ABC}(203)P_{C}(0) + 2P_{ABC}(303)P_{C}(0) + P_{ABC}(003)P_{C}(0) + P_{ABC}(013)P_{C}(0) + \cdots \\
    \cdots + P_{ABC}(020)P_{C}(2) + P_{ABC}(022)P_{C}(2) + P_{ABC}(023)P_{C}(0) + P_{ABC}(023)P_{C}(2) + \cdots \\
    \cdots + P_{ABC}(030)P_{C}(2) + P_{ABC}(031)P_{C}(2) + P_{ABC}(032)P_{C}(2) + P_{ABC}(033)P_{C}(0) + \cdots \\
    \cdots + P_{ABC}(033)P_{C}(2) + P_{ABC}(103)P_{C}(0) + P_{ABC}(113)P_{C}(0) + P_{ABC}(123)P_{C}(0) + \cdots \\
    \cdots + P_{ABC}(133)P_{C}(0) + P_{ABC}(200)P_{C}(0) + P_{ABC}(200)P_{C}(1) + P_{ABC}(200)P_{C}(2) + \cdots \\
    \cdots + P_{ABC}(200)P_{C}(3) + P_{ABC}(201)P_{C}(0) + P_{ABC}(201)P_{C}(1) + P_{ABC}(201)P_{C}(2) + \cdots \\
    \cdots + P_{ABC}(201)P_{C}(3) + P_{ABC}(203)P_{C}(1) + P_{ABC}(203)P_{C}(2) + P_{ABC}(203)P_{C}(3) + \cdots \\
    \cdots + P_{ABC}(213)P_{C}(0) + P_{ABC}(223)P_{C}(0) + P_{ABC}(300)P_{C}(0) + P_{ABC}(300)P_{C}(1) + \cdots \\
    \cdots + P_{ABC}(300)P_{C}(2) + P_{ABC}(300)P_{C}(3) + P_{ABC}(301)P_{C}(0) + P_{ABC}(301)P_{C}(1) + \cdots \\
    \cdots + P_{ABC}(301)P_{C}(2) + P_{ABC}(301)P_{C}(3) + P_{ABC}(302)P_{C}(1) + P_{ABC}(303)P_{C}(1) + \cdots \\
    \cdots + P_{ABC}(303)P_{C}(2) + P_{ABC}(303)P_{C}(3) + P_{ABC}(313)P_{C}(0) - P_{ABC}(000)P_{C}(3) \geq 0
    \end{gathered}
    \end{equation*}
    By construction, every distribution $\prob[ABC]$ that is compatible with the Triangle Structure (i.e. factorizes according to \cref{eq:compatibility_as_factorization}) must satisfy \cref{eq:ww_ineq}. As a demonstration, the Fritz distribution violates \cref{eq:ww_ineq}. Notice the final term $\prob[ABC]\br{000}\prob[C]\br{3}$ has a coefficient $-1$. For the Fritz distribution, $\prob[ABC]\br{000}\prob[C]\br{3} = \f{1}{128}\br{2 + \sqrt{2}} \simeq 0.0267$ but all of the remaining terms in \cref{eq:ww_ineq} sum to $\simeq 0.0136$ meaning that the Fritz distribution violates this inequality with violation $-0.0129\ldots \not \geq 0$. Consequently we conclude that the Fritz distribution is incompatible with the Triangle Structure, a fact that was previously only demonstrated without the use of causal compatibility inequalities.

@@

    In order to understand the importance of \cref{eq:ww_ineq}, there are a couple of important concepts to understand. First, the Fritz distribution was originally known to be incompatible with the Triangle structure due to the perfect correlation between $C$ and the measurement pseudo-settings $A_l, B_l$. The inequality of \cref{eq:ww_ineq} represents a significant advancement in our understanding of non-classicality in the Triangle structure. For example, \cref{eq:ww_ineq} is violated by distributions that do not exhibit perfect correlation between $C$ and $A_l, B_l$. Furthermore, the existence of an inequality capable of witnessing Fritz distribution \textit{is guaranteed}, albeit there was \textit{no guarantee} that the Inflation Technique would be capable of producing such an inequality. In fact, \cref{eq:ww_ineq} was derived using the Wagon-Wheel inflation depicted in \cref{fig:wagon_wheel_inflation}; smaller inflations of the Triangle structure such as the Spiral inflation (\cref{fig:spiral_inflation}) and Cut inflation (\cref{fig:cut_inflation}) are \textit{not} able to produce causal compatibility inequalities that witness the Fritz distribution. This result demonstrates that the Inflation Technique is the first tool-set powerful enough to produce causal compatibility inequalities such as \cref{eq:ww_ineq} strong enough to witness incompatible quantum distributions for the Triangle Structure. More universally, this result shows that the Inflation Technique is a promising tool for understanding quantum non-classical in more general causal structures.

    In addition to \cref{eq:ww_ineq}, numerous independent inequalities were derived for the Triangle Structure that are violated by the Fritz distribution. The majority of these inequalities share most or all of the qualitative features of \cref{eq:ww_ineq}, and hence those inequalities are omitted from this manuscript. Instead, we present \cref{eq:web_inequality}, another causal compatibility inequality for the Triangle structure that is violated by the Fritz distribution and was produced using the \cref{fig:the_web_inflation} --- a considerably larger inflation than the Wagon-Wheel inflation. Note that in \cref{eq:web_inequality} $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$.

@@

    The inequalities presented above (\cref{eq:ww_ineq,eq:web_inequality}) were curated to demonstrate the incompatibility of the Fritz distribution in particular. To reiterate, the Fritz distribution is incompatible with the Triangle Structure because it assigns a unique role to one of the variables, specifically $C$. The asymmetry within the Fritz distribution is reflected in the asymmetry of \cref{eq:ww_ineq,eq:web_inequality}. In order to discover new forms of non-classicality in the Triangle Structure, it is desirable to obtain measures of non-classicality (i.e. inequalities) that do not admit this bias. In an effort to find a causal compatibility inequality qualitatively distinct from \cref{eq:ww_ineq,eq:web_inequality}, we developed a technique to derive inequalities with certain symmetry properties such as \cref{eq:symmetic_web_inequality} which is symmetric with respect to any permutation of the variables $A, B, C$. These techniques are explained in \cref{sec:symmetric_inequalities}. Surprisingly, \cref{eq:symmetic_web_inequality} is also violated by the Fritz distribution.
    \begin{equation}
        \label{eq:symmetic_web_inequality}
        \includegraphics[width=\linewidth]{../../figures/inequalities/MosekCertFritzSym_ineq_standalone}
    \end{equation}
    Note that $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$ and $\bs{P(113)P(330)}_3$ is shorthand for a sum the over permutations of $A,B,C$, i.e. $\bs{P(113)P(330)}_3 \defined P(113)P(330) + P(131)P(303) + P(311)P(033)$.

    Most importantly, these causal compatibility inequalities are a positive resolution of Fritz's problem from \cref{sec:fritz_distribution}. These inequalities are derived without making use of Bell's theorem and instead uses the Inflation Technique to approach non-classicality from a causal inference perspective. Additionally, the derivation of causal compatibility inequalities allows one prove incompatibility even when perfect correlations are absent.

    \section{Numerical Optimizations \& Noisy Distributions}
    \label{sec:violations_noise}
    Causal compatibility inequalities for the Triangle structure (such as those derived in \cref{sec:deriving_inequalities}) offer an avenue into studying quantum non-classicality. In this section, we make use of two methods, exposure to noise and numerical optimization, to further understand the nature of quantum non-classicality in connection to compatibility inequalities. In order to compare different inequalities simultaneously, our convention is to rearrange each inequality $I$ so $I\br{\prob} < 0$ represent a violation of $I$ while $I\br{\prob} \leq 0$ represents satisfaction of $I$ (with $I\br{\prob} = 0$ corresponding to complete saturation of the inequality). For the subsequent analysis, $4$ inequalities where chosen. First, $I_0$ is the inequality derived using the Wagon-Wheel wheel inflation \cref{eq:ww_ineq}. The other three inequalities $I_1, I_2, I_3$ were all derived using the Web inflation; $I_1$ can be found in \cref{eq:web_inequality} while $I_3$ is the symmetric inequality in \cref{eq:symmetic_web_inequality}. Inequality $I_2$ is not reproduced anywhere in this document but is similar to \cref{eq:web_inequality}.

@@

    \subsection{Numerical Optimizations}
    \label{sec:optimizations}
    \todo[TC]{Determine if I should remove this paragraph or shorten it}
    Causal compatibility inequalities act as a \textit{measure} of non-classicality. If two non-classical distributions $\prob[1]$ and $\prob[2]$ violate the same inequality $I$ with violations $I\br{\prob[1]}$ and $I\br{\prob[2]}$ respectively, it is somewhat reasonable to say that $\prob[1]$ is \textit{more} non-classical than $\prob[2]$ whenever ${I\br{\prob[1]}} < I\br{\prob[2]}$. However, this statement is accompanied by a few caveats. First, it is possible (and frequently the case) for ${I\br{\prob[1]}} < I\br{\prob[2]}$ to hold for one inequality $I$ but have ${\ti I\br{\prob[2]}} < \ti I\br{\prob[1]}$ hold for another inequality $\ti I$. In this case, all one can claim is that $\prob[1]$ is more incompatible than $\prob[2]$ with respective to $I$ but the contrary is true with respect to $\ti I$. Second, not all inequalities $I$ are \textit{good} measures of non-classicality. In the case of the Bell structure, the linear inequality constraints associated with the facets of the marginal polytope are the best measures of non-classicality because the facets form a necessary and sufficient of constraints with all other inequalities following from positive mixtures. However, good measures of incompatibility are less understood in the Triangle structure where the space of classical correlations is non-convex. At the very least, the inequalities derived in this report are likely \textit{not} the best measures of incompatibility simply because they have be curated toward the Fritz distribution. Nonetheless, these inequalities act the \textit{first} measures of non-classicality in the Triangle structure.

    In order to find quantum distributions that are more non-classical than the Fritz, we performed numerical optimizations against each inequality $I$ by parameterizing the space of quantum-accessible probability distributions that can be realized on the Triangle Structure \cref{fig:triangle_structure} and thus expressed as follows:
    \[ \prob[\p{ABC}]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}} \netperm M_{\p{A},a}\otimes M_{\p{B},b} \otimes M_{\p{C},c}} \eq \label{eq:quantum_model_triangle}\]
    Where $\rho_{\p{AB}}, \rho_{\p{BC}}, \rho_{\p{CA}}$ are bipartite density matrices, $M_{\p{A}}, M_{\p{B}}, M_{\p{C}}$ are generic measurements sets and $\netperm$ is a permutation matrix that aligns the states and measurements appropriately. In order to parameterize all such distributions, we elect to parameterize the states and measurements separately. In order to qualify the scope of \cref{eq:quantum_model_triangle} and associated computational complexity of the parameterization, there are a two restrictions that are made with justification. Motivated by the fact that the Fritz distribution (\cref{sec:fritz_distribution}) only requires qubit states, the states $\rho$ are taken to be bipartite \textit{qubit} states. Qubit states are more computationally feasible compared to $n$-dimensional states whereby the joint density matrix $\rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}}$ becomes an $n^6 \times n^6$ matrix. Additionally, we restrict our focus to projective-valued measures (PVMs) instead of projective-operator valued measures (POVMs) for three reasons. First, \cref{sec:fritz_distribution} demonstrates that PVMs are sufficient for witnessing incompatible quantum distributions in the Triangle structure. Second, although generating $k$-outcome POVM measurements is possible using rejection sampling techniques~\cite{Petz_2015}, a valid, unbiased parameterization was not found for $k > 2$. Finally, PVMs provide considerable computational advantage over POVMs as they permit \cref{eq:quantum_model_triangle} to be re-written as \cref{eq:quantum_model_triangle_pvms}.
    \[ \prob[\p{ABC}]\br{abc} = \bramidket{m_{\p{A},a}m_{\p{B},b}m_{\p{C},c}}{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm}{m_{\p{A},a}m_{\p{B},b}m_{\p{C},c}} \eq \label{eq:quantum_model_triangle_pvms}\]

@@

    \subsection{Rosset Variation}
    \label{sec:rosset_variation}
    \todo[TC]{This might take a page}

@@

    Fritz's Problem is concerned with identifying incompatible quantum distributions in the Triangle structure that are qualitatively different than the non-classical distributions of the Bell structure discussed in \cref{sec:bell_structure}. When specifically concerned with entanglement resources, Bell structure non-classicality exploits the entanglement of a single bipartite quantum state. In the Triangle structure, the observable nodes $A,B,C$ have access to potentially three different bipartite quantum states. As noted in \cref{sec:fritz_distribution}, the Fritz distribution can be implemented using only a single entangled state\footnote{Of course there exists implementations that make use of three entangled states but at minimum only one is necessary.}. The question, as proposed by \ref{r:2}, remains: does there exist incompatible quantum distributions that genuinely require the entanglement resources of three states? At first, one might suspect that finding such distributions would affirmatively demonstrate a new form of entanglement resource distinct to the Triangle structure. Unfortunately, this is simply not the case. By increasing the cardinality of the outcomes for $A, B, C$, it is possible to generate a distribution that is non-classical yet quantum and requires all three of the shared resources to be entangled. This can be accomplished by superimposing three copies of statistically independent Fritz distributions to the Triangle Structure, each of which utilizes a distinct party to announce the corresponding measurement pseudo-settings. Such a distribution would be of the form described by \ref{r:2} because under this construction, the removal of any entangled resource would render the distribution quantum-inaccessible.\footnote{This insight was originally made by Miguel Navascués in private communications.} Consequently, it becomes desirable to find non-classical quantum correlations for the Triangle Structure which have the fewest number of outcomes.

@@

    \subsection{Exemplary Inflations of The Triangle Structure}
    \label{sec:exemplary_inflations_of_the_triangle structure}

>>>>

\begin{document}
    \title{Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle structure}
    \author{Thomas C. Fraser}
    \email{tcfraser@tcfraser.com}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
    \affiliation{University of Waterloo, Waterloo, Ontario, Canada, N2L 3G1}
    \author{Elie Wolfe}
    \affiliation{Perimeter Institute for Theoretical Physics, Waterloo, Ontario, Canada, N2L 2Y5}
    % \email{ewolfe@perimeterinstitute.ca}
    \date{\today}
    \begin{abstract}
        It has long been recognized that certain quantum correlations are incompatible with particular assumption about classical causal structure. Given a causal structure of unknown classicality, the presence of such correlations certifies the non-classical nature of the causal structure in a device independent fashion. In the context of two parties sharing a common resource, these non-classical correlations are also known as non-local correlations. Any constraint which is satisfied by all correlations which \textit{are} classically compatible with a given causal structure defines a causal compatibility criterion. Such criteria were recently were recently derived for the Triangle structure [\href[pdfnewwindow]{http://arxiv.org/abs/1609.00672}{arXiv:1609.00672}] in the form of polynomial inequalities, begging the question: do any of those inequalities admit violation by quantum correlations? Numerical investigation suggests not, and we further conjecture that the set of correlations admitted by the classical Triangle structure is equivalent to the set of correlations admitted by its quantum generalization whenever the three observable variables are binary. Our main contribution in this work, however, is the derivation of new causal compatibility inequalities for the Triangle structure which \textit{do} admit quantum violation. We conclude by considering the possibility of quantum resources potentially qualitatively different from those known previously.
    \end{abstract}
    \maketitle
    \tableofcontents
    % \setlength{\parskip}{1em}

@@

    \begin{figure}
    \begin{center}
        \begin{minipage}[t]{.48\textwidth}
            \centering
            \scalebox{1.0}{\input{../../figures/causal_structures/bell_scenario}}
            \caption{The Bell structure consisting of two observers $\p{A}, \p{B}$ together with measurement settings $S_{\p{A}}$ and $S_{\p{B}}$ respectively. The shared hidden variable is labeled $\la$.}
            \label{fig:bell_scenario}
        \end{minipage}\hspace{0.04\textwidth}%
        \begin{minipage}[t]{.48\textwidth}
            \centering
            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_structure}}
            \caption{The casual structure of the Triangle structure. Three variables $A,B,C$ are observable, while $X, Y, Z$ are latent variables.}
            \label{fig:triangle_structure}
        \end{minipage}
    \end{center}
    \end{figure}
    \section{Triangle structure}
    \label{sec:triangle_structure}

@@

    \section{Triangle structure Inequalities}
    \label{sec:found_inequalities}

    \Cref{sec:causal_compatibility} defined causal compatibility inequalities while \cref{sec:fritz_distribution} recalled and discussed the Fritz distribution together with a brief summary of its incompatibility with the Triangle structure. Heretofore, there were no known causal compatibility inequalities for the Triangle structure that were capable of witnessing the non-classicality of any quantum distributions~\cite{Inflation}. By leveraging the incompatibility of the Fritz distribution~\cite{Fritz_2012} and tools provided by the Inflation Technique~\cite{Inflation}, we have obtained numerous causal compatibility inequalities for the Triangle structure that are violated by the Fritz distribution. A representative sample of these inequalities are presented here. The methods used to derive these inequalities are largely based on the Inflation Technique~\cite{Inflation}. A summary of the Inflation Technique and other methods used will be deferred to \cref{sec:inflation_technique} where unfamiliar readers will find a succinct yet sufficient presentation of the requisites.

    The first causal compatibility inequality is reported below:
    \begin{equation*}
    \begin{gathered}
    \eq\label{eq:ww_ineq}
    2P_{ABC}(203)P_{C}(0) + 2P_{ABC}(303)P_{C}(0) + P_{ABC}(003)P_{C}(0) + P_{ABC}(013)P_{C}(0) + \cdots \\
    \cdots + P_{ABC}(020)P_{C}(2) + P_{ABC}(022)P_{C}(2) + P_{ABC}(023)P_{C}(0) + P_{ABC}(023)P_{C}(2) + \cdots \\
    \cdots + P_{ABC}(030)P_{C}(2) + P_{ABC}(031)P_{C}(2) + P_{ABC}(032)P_{C}(2) + P_{ABC}(033)P_{C}(0) + \cdots \\
    \cdots + P_{ABC}(033)P_{C}(2) + P_{ABC}(103)P_{C}(0) + P_{ABC}(113)P_{C}(0) + P_{ABC}(123)P_{C}(0) + \cdots \\
    \cdots + P_{ABC}(133)P_{C}(0) + P_{ABC}(200)P_{C}(0) + P_{ABC}(200)P_{C}(1) + P_{ABC}(200)P_{C}(2) + \cdots \\
    \cdots + P_{ABC}(200)P_{C}(3) + P_{ABC}(201)P_{C}(0) + P_{ABC}(201)P_{C}(1) + P_{ABC}(201)P_{C}(2) + \cdots \\
    \cdots + P_{ABC}(201)P_{C}(3) + P_{ABC}(203)P_{C}(1) + P_{ABC}(203)P_{C}(2) + P_{ABC}(203)P_{C}(3) + \cdots \\
    \cdots + P_{ABC}(213)P_{C}(0) + P_{ABC}(223)P_{C}(0) + P_{ABC}(300)P_{C}(0) + P_{ABC}(300)P_{C}(1) + \cdots \\
    \cdots + P_{ABC}(300)P_{C}(2) + P_{ABC}(300)P_{C}(3) + P_{ABC}(301)P_{C}(0) + P_{ABC}(301)P_{C}(1) + \cdots \\
    \cdots + P_{ABC}(301)P_{C}(2) + P_{ABC}(301)P_{C}(3) + P_{ABC}(302)P_{C}(1) + P_{ABC}(303)P_{C}(1) + \cdots \\
    \cdots + P_{ABC}(303)P_{C}(2) + P_{ABC}(303)P_{C}(3) + P_{ABC}(313)P_{C}(0) - P_{ABC}(000)P_{C}(3) \geq 0
    \end{gathered}
    \end{equation*}
    By construction, every distribution $\prob[ABC]$ that is compatible with the Triangle structure (i.e. factorizes according to \cref{eq:compatibility_as_factorization}) must satisfy \cref{eq:ww_ineq}. As a demonstration, the Fritz distribution violates \cref{eq:ww_ineq}. Notice the final term $\prob[ABC]\br{000}\prob[C]\br{3}$ has a coefficient $-1$. For the Fritz distribution, $\prob[ABC]\br{000}\prob[C]\br{3} = \f{1}{128}\br{2 + \sqrt{2}} \simeq 0.0267$ but all of the remaining terms in \cref{eq:ww_ineq} sum to $\simeq 0.0136$ meaning that the Fritz distribution violates this inequality with violation $-0.0129\ldots \not \geq 0$. Consequently we conclude that the Fritz distribution is incompatible with the Triangle structure, a fact that was previously only demonstrated without the use of causal compatibility inequalities.

@@

    In order to understand the importance of \cref{eq:ww_ineq}, there are a couple of important concepts to understand. First, the Fritz distribution was originally known to be incompatible with the Triangle structure due to the perfect correlation between $C$ and the measurement pseudo-settings $A_l, B_l$. The inequality of \cref{eq:ww_ineq} represents a significant advancement in our understanding of non-classicality in the Triangle structure. For example, \cref{eq:ww_ineq} is violated by distributions that do not exhibit perfect correlation between $C$ and $A_l, B_l$. Furthermore, the existence of an inequality capable of witnessing Fritz distribution \textit{is guaranteed}, albeit there was \textit{no guarantee} that the Inflation Technique would be capable of producing such an inequality. In fact, \cref{eq:ww_ineq} was derived using the Wagon-Wheel inflation depicted in \cref{fig:wagon_wheel_inflation}; smaller inflations of the Triangle structure such as the Spiral inflation (\cref{fig:spiral_inflation}) and Cut inflation (\cref{fig:cut_inflation}) are \textit{not} able to produce causal compatibility inequalities that witness the Fritz distribution. This result demonstrates that the Inflation Technique is the first tool-set powerful enough to produce causal compatibility inequalities such as \cref{eq:ww_ineq} strong enough to witness incompatible quantum distributions for the Triangle structure. More universally, this result shows that the Inflation Technique is a promising tool for understanding quantum non-classical in more general causal structures.

    In addition to \cref{eq:ww_ineq}, numerous independent inequalities were derived for the Triangle structure that are violated by the Fritz distribution. The majority of these inequalities share most or all of the qualitative features of \cref{eq:ww_ineq}, and hence those inequalities are omitted from this manuscript. Instead, we present \cref{eq:web_inequality}, another causal compatibility inequality for the Triangle structure that is violated by the Fritz distribution and was produced using the \cref{fig:the_web_inflation} --- a considerably larger inflation than the Wagon-Wheel inflation. Note that in \cref{eq:web_inequality} $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$.

@@

    The inequalities presented above (\cref{eq:ww_ineq,eq:web_inequality}) were curated to demonstrate the incompatibility of the Fritz distribution in particular. To reiterate, the Fritz distribution is incompatible with the Triangle structure because it assigns a unique role to one of the variables, specifically $C$. The asymmetry within the Fritz distribution is reflected in the asymmetry of \cref{eq:ww_ineq,eq:web_inequality}. In order to discover new forms of non-classicality in the Triangle structure, it is desirable to obtain measures of non-classicality (i.e. inequalities) that do not admit this bias. In an effort to find a causal compatibility inequality qualitatively distinct from \cref{eq:ww_ineq,eq:web_inequality}, we developed a technique to derive inequalities with certain symmetry properties such as \cref{eq:symmetic_web_inequality} which is symmetric with respect to any permutation of the variables $A, B, C$. These techniques are explained in \cref{sec:symmetric_inequalities}. Surprisingly, \cref{eq:symmetic_web_inequality} is also violated by the Fritz distribution.
    \begin{equation}
        \label{eq:symmetic_web_inequality}
        \includegraphics[width=\linewidth]{../../figures/inequalities/MosekCertFritzSym_ineq_standalone}
    \end{equation}
    Note that $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$ and $\bs{P(113)P(330)}_3$ is shorthand for a sum the over permutations of $A,B,C$, i.e. $\bs{P(113)P(330)}_3 \defined P(113)P(330) + P(131)P(303) + P(311)P(033)$.

    Most importantly, these causal compatibility inequalities are a positive resolution of Fritz's problem from \cref{sec:fritz_distribution}. These inequalities are derived without making use of Bell's theorem and instead uses the Inflation Technique to approach non-classicality from a causal inference perspective. Additionally, the derivation of causal compatibility inequalities prove incompatibility even when perfect correlations are absent.

    \section{Numerical Optimizations \& Noisy Distributions}
    \label{sec:violations_noise}
    Causal compatibility inequalities, including those derived in \cref{sec:found_inequalities}, offer an avenue into studying quantum non-classicality. Ultimately, the motivation for finding these inequalities is binary: the first is to classify differing distributions by their compatibility with a given causal structure, and the second is to measure the degree in which a given distribution is non-classical. This approach has been well-studied in the Bell structure, where extremal non-classical correlations maximally violate Bell inequalities~\cite{PR_1995}. However, inequalities are just a singular example of numerous distinct measures of non-classicality~\cite[Section 5]{Vicente_2014}. Alternatives include measuring the non-local content, robustness to noise, or even the classical simulation cost of a given distribution. For previously studied causal structures, such as the Bell structure, there exists a uncertainty toward which measure of non-classicality is best. The inequalities derived in this report are likely \textit{not} the best measures of non-classicality simply because they have be curated toward the Fritz distribution. Nonetheless, these inequalities act the \textit{first} measures of non-classicality in the Triangle structure to be found that admit quantum violations. In this section, two measures are used that make use of these compatibility inequalities: robustness to noise and direct numerical violation.

    To compare different inequalities simultaneously, our convention is to rearrange each inequality $I$ such that $I\br{\prob} < 0$ indicates violation of $I$ while $I\br{\prob} \leq 0$ indicates satisfaction of $I$ (with $I\br{\prob} = 0$ corresponding to complete saturation of the inequality). For the subsequent analysis, $4$ inequalities where chosen. First, $I_0$ is the inequality derived using the Wagon-Wheel wheel inflation \cref{eq:ww_ineq}. The other three inequalities $I_1, I_2, I_3$ were all derived using the Web inflation; $I_1$ can be found in \cref{eq:web_inequality} while $I_3$ is the symmetric inequality in \cref{eq:symmetic_web_inequality}. Inequality $I_2$ is not reproduced anywhere in this document but is similar to \cref{eq:web_inequality}.

@@

    \subsection{Numerical Optimizations}
    \label{sec:optimizations}

    In order to find quantum distributions that are more non-classical than the Fritz, we performed numerical optimizations against each inequality $I$ by parameterizing the space of quantum-accessible probability distributions that can be realized on the Triangle structure (\cref{fig:triangle_structure}) and thus expressed as follows:
    \[ \prob[\p{ABC}]\br{abc} = \Tr\bs{\netperm^\intercal \rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}} \netperm M_{\p{A},a}\otimes M_{\p{B},b} \otimes M_{\p{C},c}} \eq \label{eq:quantum_model_triangle}\]
    Where $\rho_{\p{AB}}, \rho_{\p{BC}}, \rho_{\p{CA}}$ are bipartite density matrices, $M_{\p{A}}, M_{\p{B}}, M_{\p{C}}$ are generic measurements sets and $\netperm$ is a permutation matrix that aligns the states and measurements appropriately. In order to parameterize all such distributions, we elect to parameterize the states and measurements separately. In order to qualify the scope of \cref{eq:quantum_model_triangle} and associated computational complexity of the parameterization, there are a two restrictions that are made with justification. Motivated by the fact that the Fritz distribution (\cref{sec:fritz_distribution}) only requires qubit states, the states $\rho$ are taken to be bipartite \textit{qubit} states. Qubit states are more computationally feasible compared to $n$-dimensional states whereby the joint density matrix $\rho_{\p{AB}}\otimes\rho_{\p{BC}}\otimes\rho_{\p{CA}}$ becomes an $n^6 \times n^6$ matrix. Additionally, we restrict our focus to projective-valued measures (PVMs) instead of projective-operator valued measures (POVMs) for three reasons. First, \cref{sec:fritz_distribution} demonstrates that PVMs are sufficient for witnessing incompatible quantum distributions in the Triangle structure. Second, although generating $k$-outcome POVM measurements is possible using rejection sampling techniques~\cite{Petz_2015}, a valid, unbiased parameterization was not found for $k > 2$. Finally, PVMs provide considerable computational advantage over POVMs as they permit \cref{eq:quantum_model_triangle} to be re-written as \cref{eq:quantum_model_triangle_pvms}.
    \[ \prob[\p{ABC}]\br{abc} = \bramidket{m_{\p{A},a}m_{\p{B},b}m_{\p{C},c}}{\netperm^\intercal \rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA} \netperm}{m_{\p{A},a}m_{\p{B},b}m_{\p{C},c}} \eq \label{eq:quantum_model_triangle_pvms}\]

@@

@@

    Fritz's Problem is concerned with identifying incompatible quantum distributions in the Triangle structure that are qualitatively different than the non-classical distributions of the Bell structure discussed in \cref{sec:bell_structure}. When specifically concerned with entanglement resources, Bell structure non-classicality exploits the entanglement of a single bipartite quantum state. In the Triangle structure, the observable nodes $A,B,C$ have access to potentially three different bipartite quantum states. As noted in \cref{sec:fritz_distribution}, the Fritz distribution can be implemented using only a single entangled state.\footnote{Of course there exists implementations that make use of three entangled states but at minimum only one is necessary.} The question, as proposed by \ref{r:2}, remains: does there exist incompatible quantum distributions that genuinely require the entanglement resources of three states? At first, one might suspect that finding such distributions would affirmatively demonstrate a new form of entanglement resource distinct to the Triangle structure. Unfortunately, this is simply not the case. By increasing the cardinality of the outcomes for $A, B, C$, it is possible to generate a distribution that is non-classical yet quantum and requires all three of the shared resources to be entangled. This can be accomplished by superimposing three copies of statistically independent Fritz distributions to the Triangle structure, each of which utilizes a distinct party to announce the corresponding measurement pseudo-settings. Such a distribution would be of the form described by \ref{r:2} because under this construction, the removal of any entangled resource would render the distribution quantum-inaccessible.\footnote{This insight was originally made by Miguel Navascués in private communications.} Consequently, it becomes desirable to find non-classical quantum correlations for the Triangle structure which have the fewest number of outcomes. In pursuit of this objective, the authors were able to prove the non-classicality (using the methods described in \cref{sec:inflation_technique}) of a variant of the Fritz distribution where $C$ has only two outcomes, one corresponding to $A, B$ correlations and another corresponding to $A, B$ anti-correlations.\footnote{This variation was originally suggested by Denis Rosset in private communications.} These advancements suggest the cardinality of measurement outcomes are intimately connected to quantum non-classicality and should be a focus for future research.

@@

    \subsection{Exemplary Inflations of The Triangle structure}
    \label{sec:exemplary_inflations_of_the_triangle structure}
